Review stages

### 2024-05-13 doc/review-stages.qmd
refactor: moved code from quarto into own function file

```{r setup}
#| include: false
library(tidyverse)
library(here)
library(fs)
```

@@

```{r}
#| message: false
title_reviews <- here("data/review/titles/") |>
  dir_ls(glob = "*.csv") |>
  map(read_csv)

reviewers <- names(title_reviews) |>
  path_file() |>
  path_ext_remove() |>
  str_to_sentence()

title_reviews <- title_reviews |>
  set_names(reviewers)
```

@@

```{r tbl-titles-kept}
#| message: false
#| tbl-cap: "Number of articles each reviewer kept after the first screening of the titles."
title_reviews |>
  map(\(df) count(df, name = "Articles kept")) |>
  list_rbind(names_to = "Reviewers") |>
  # TODO: Include percent of total articles.
  knitr::kable()
```

We want to know how many of these titles we all agreed on between the
three reviewers, which is shown in @tbl-titles-agreements

```{r}
common_titles <- title_reviews |>
  reduce(\(df1, df2) {
    inner_join(df1, df2, by = join_by(id, title, publication_date, doi))
  })

#| tbl-cap: "Number of articles we all agreed on."
common_titles |>
  count(name = "Titles all agreed on") |>
  knitr::kable()

```

@@

```{r tbl-title-disagreements}
#| tbl-cap: "Article titles **not** kept between all reviewers during the title screening stage."
title_reviews |>
  map(\(df) anti_join(df, common_titles, by = join_by(id, title, publication_date, doi))) |>
  list_rbind() |>
  select("Article titles" = title) |>
  distinct() |>
  knitr::kable()
```

We saved a new csv file with all the disagreements and saved a new list
called "resolved.csv" where the final papers to include are listed.

```{r csv-paper-disagreements}

title_disagrements <- title_reviews |>
  map(\(df) anti_join(df, common_titles, by = join_by(id, title, publication_date, doi))) |>
  list_rbind() |>
  distinct()

#save new csv file to go through links and check disagreements
write.table(title_disagrements, file = here("data/review/titles/disagreements.csv"))

```

>>>>

```{r setup}
#| include: false
library(tidyverse)
library(here)
library(fs)
targets::tar_config_set(store = here("_targets"))
```

@@

```{r}
#| message: false
```

@@

```{r tbl-titles-kept}
#| message: false
#| tbl-cap: "Number of articles each reviewer kept after the first screening of the titles."
targets::tar_read(titles_kept) |>
  map(\(df) count(df, name = "Articles kept")) |>
  list_rbind(names_to = "Reviewers") |>
  # TODO: Include percent of total articles.
  knitr::kable()
```

We want to know how many of these titles we all agreed on between the
three reviewers:

```{r}
common_titles <- targets::tar_read(titles_agreed_on)
```

We seemed to agree on `r nrow(common_titles)` titles, with the full
title list shown in @tbl-titles-agreements.

@@

```{r tbl-title-disagreements}
#| tbl-cap: "Article titles **not** kept between all reviewers during the title screening stage."
targets::tar_read(titles_disagreed_on) |>
  select("Article titles" = title) |>
  knitr::kable()
```

We saved a new csv file with all the disagreements and then made a copy
of that list in the file `resolved.csv`. This file contains some titles
that we disagreed on but that were briefly reviewed by one reviewer,
discussed, and included in the end.

The titles we agreed on were:

```{r}
#| tbl-cap: "Article titles we agreed to keep from the disagreement list."
targets::tar_read(titles_resolved_path) |>
  select("Article title" = title) |>
  knitr::kable()
```
